DATA 624 Project 2

### 2020-05-10 DATA624/Project 2 Personal Work.Rmd
More work on Group 2

```{r setup, echo=FALSE, cache=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = TRUE, comment = NA, message = FALSE, warning = FALSE)
library(tidyverse)
library(tidyr)
library(kableExtra)
library(corrplot)
library(caret)
library(scales)
library(readxl)
library(naniar)
library(xgboost)
library(Matrix)
knitr::knit_hooks$set(inline = function(x) {
  if (!is.numeric(x)) {
    x
  } else {
    prettyNum(round(x, 2), big.mark = ",")
  }
})
options(scipen = 999)
seed <- 42
```

@@

```{r knn_impute}
set.seed(seed)
impute_model <- df %>%
  select(-PH) %>%
  preProcess(., method = "knnImpute")

df_imputed <- predict(impute_model, df) %>%
  na.omit()

eval_df_imputed <- predict(impute_model, eval_df)
```

@@

```{r ranger_rf}
set.seed(seed)
tc <- trainControl(method = "cv", number = 10)
rf_fit <- train(PH ~ ., data = train_df_imputed, method = "ranger", importance = "permutation", trControl = tc)
rf_fit

@@

```{r rf, cache=TRUE}
set.seed(seed)
rf_fit2 <- train(PH ~ ., data = train_df_imputed, method = "rf", trControl = tc)
rf_fit2

@@

>>>>

```{r setup, echo=FALSE, cache=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = TRUE, comment = NA, message = FALSE, warning = FALSE)
library(tidyverse)
library(tidyr)
library(kableExtra)
library(corrplot)
library(caret)
library(scales)
library(readxl)
library(naniar)
library(xgboost)
library(Matrix)
library(VIM)
knitr::knit_hooks$set(inline = function(x) {
  if (!is.numeric(x)) {
    x
  } else {
    prettyNum(round(x, 2), big.mark = ",")
  }
})
options(scipen = 999)
seed <- 12345
```

@@

```{r knn_impute}
set.seed(seed)

df_imputed <- kNN(df, imp_var = FALSE)
eval_df_imputed <- kNN(select(eval_df, -PH), imp_var = FALSE)
```

@@

```{r ranger_rf}
set.seed(seed)
tc <- trainControl(method = "cv", number = 10, allowParallel = TRUE)
rf_fit <- train(PH ~ ., data = train_df_imputed, method = "ranger", importance = "permutation", trControl = tc)
rf_fit

@@

```{r rf}
set.seed(seed)
rf_fit2 <- train(PH ~ ., data = train_df_imputed, method = "rf", trControl = tc)
rf_fit2

@@

## Stepwise Linear Regression

```{r stepwise}
# Loading latter to avoid the select clash with dplyr
library(MASS)
full_model <- lm(PH ~., data = train_df_imputed)
# Stepwise regression model
lm_model <- stepAIC(full_model, direction = "both", trace = FALSE)
summary(lm_model)
```

```{r}
set.seed(seed)
tc <- trainControl(method = "cv", number = 10, allowParallel = TRUE)
lm_fit <- train(PH ~ ., data = train_df_imputed, method = "glmStepAIC", trControl = tc)
lm_fit

varImp(lm_fit)

lm_predictions <- predict(lm_fit, test_df_imputed)
postResample(pred = lm_predictions, obs = test_df_imputed$PH)
```
